---
title: "Scatterplots in R"
author: "ashin"
date: "05/05/2020"
output:
  word_document: default
---


Here we will look how to create scatterplots using R language
So lets Start.
Library used= ggplot2
(to install, install.packages("ggplot2"))
Dataset=mtcars(Inbuilt)


## Basic Scatter Plot



```{r}
library(ggplot2)
 ggplot(mtcars, aes(x=mpg,y=wt))+geom_point(shape=19)
```
 

This code gives the basic scatter plot.


## By adding a 3rd variable


```{r}
library(ggplot2)
mtcars$cylFactor <- factor(mtcars$cyl)
ggplot(mtcars, aes(x=mpg,y=wt,shape=cylFactor)) + geom_point()
```

## Adding the desired colour to the plot



```{r}
library(ggplot2)
ggplot(mtcars, aes(x=mpg,y=wt,colour="red")) + geom_point()

```

By this we can add a desired colour to the plot.

## Combining the 3rd variable and colour

```{r}
library(ggplot2)
mtcars$cylFactor <- factor(mtcars$cyl)
 ggplot(mtcars, aes(x=mpg,y=wt,shape=cylFactor,colour="red")) + geom_point()
```

Here we are able to see that colour does not affect much when wee add a 3rd variable here.Now lets check how we can add a 3rd varible by defining colour.

## Add a 3rd variable by colour



```{r}
library(ggplot2)
mtcars$cylFactor <- factor(mtcars$cyl)
ggplot(mtcars, aes(x=mpg,y=wt,colour=cylFactor)) + geom_point()
```
This looks good. Now lets label all the axis and complete the scatter plot


## Final Plot




```{r}
library(ggplot2)
mtcars$cylFactor <- factor(mtcars$cyl)
ggplot(mtcars,aes(x=mpg,y=wt,color=cylFactor))  +geom_point(shape=19) +xlab("Miles Per Gallon") +ylab("Weight") +labs(colour = "Cylinders") +ggtitle("Scatterplot")
```


By this we have come across how to create scatterplot using r language and I hope everyone got this.




